---
title: Summary of Synthetic Variables Estimation 
subtitle: EES 2019 Voter Study (Belgian, Bulgarian, Cypriot, and Italian samples)
author: Giuseppe Carteny
date: 05.04.2022 
toc: false
output: 
  bookdown::pdf_document2:
    includes:
      in_header: eval_header.tex
urlcolor: RedOrange
---

```{r echo=FALSE, warning=FALSE, message=FALSE}

# Load 'here' for sourcing # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
library('here')

# Source the general workflow # - - - - - - - - - - - - - - - - - - - - - - - - - - - - -#
source(here('Scripts', 'synteval_scripts', 'Synteval_gen.R'))

```

\newpage
# Bulgaria

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Source the Cypriot synteval script # - - - - - - - - - - - - - - - - - - - - - - - - - #

source(here('Scripts', 'synteval_scripts', 'country_spec_scripts', 'EES2019_bg_synteval.R'))

```

Synthetic variables have been estimated for the full set of relevant parties available in the original 
2019 EES Bulgarian voter study (Table \ref{table:relprty_tab_bg}) selected according to the criteria 
stated in the EES 2019 SDM codebook (for the criteria see Sect. XXX). 

```{r echo=FALSE, warning=FALSE, message=FALSE}
options(knitr.kable.NA = 'NA')
options(knitr.table.format = "latex")

names(relprty_df) <- c('Dep. Var.', 'Party', 'Party name (eng)')

relprty_df %>% 
  kable(caption = "Cypriot relevant parties \\label{table:relprty_tab_bg}", booktabs = T, 
        align = c('l', 'c', 'l')) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

Full OLS models converge and coefficients do not show any particular issue (see Table 
\ref{table:full_ols_bg}). 
In terms of model fit, the adjusted coefficient of determination ($R^2$) values vary between 
a minimum value of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['Adj_Rsq']]` 
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partycode']]` 
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['Adj_Rsq']]`
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partycode']]`
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for full OLS models and null 
models suggests that only one null model performs marginally better than the full ones (see Table 
\ref{table:ols_aic_bg}).


```{r echo=FALSE, warning=FALSE, message=FALSE}


names(ols_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

ols_aic %>% 
  kable(caption = "Akaike Information Criterion values for OLS full and null models 
        \\label{table:ols_aic_bg}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))


```

On the contrary, four out of seven logistic regression models (see Table \ref{table:full_logit_bg}) show 
inflated standard errors for some of the coefficients of interest, in particular: 

* Model 9: D8_rec;
* Model 10a: D7_rec;
* Model 13a: EDU_rec;
* Model 14a: D7_rec and D8_rec.

In Model 3 the constant term and other regression coefficients are not affected by said inflated 
standard errors, whereas the remaining ones present a more problematic profile. 
Inflated standard errors due to separation issues affect all th models. In short: 

* No respondents from rural areas voted for party 302 (Table \ref{table:crosstab_1_bg});
* No upper middle or upper class respondents voted for party 303 (Table \ref{table:crosstab_2_bg}); 
* No low educated people voted for party 306 (Table \ref{table:crosstab_3_bg});
* No upper middle or upper class respondents and living in rural areas ones voted for party 307 
(Table \ref{table:crosstab_4_bg});

As a consequence, constrained versions of the models just mentioned above have been estimated, 
removing the variables source of misfit. Likelihood-ratio test results show that $H_0$ can be rejected 
only for Model 2, while in all the other cases the null hypothesis cannot be rejected. 

Consequently, synthetic variables for respondents' vote choice for parties 303, 306, and 307 have been 
generated relying on the constrained models (Models 9b, 10b, 13b, 14b). 

```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = '')

anova_lst[[1]] %>%
  kable(caption = "Likelihood-ratio Test between Model 9a (Unconstrained) and Model 9b (Constrained)
                  \\label{table:lrtest_1_bg}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

anova_lst[[2]] %>%
  kable(caption = "Likelihood-ratio Test between Model 10a (Unconstrained) and Model 10b (Constrained)
                  \\label{table:lrtest_2_bg}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

anova_lst[[3]] %>%
  kable(caption = "Likelihood-ratio Test between Model 13a (Unconstrained) and Model 13b (Constrained)
                  \\label{table:lrtest_3_bg}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

anova_lst[[4]] %>%
  kable(caption = "Likelihood-ratio Test between Model 14a (Unconstrained) and Model 14b (Constrained)
                  \\label{table:lrtest_4_bg}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

In terms of model fit (Table \ref{table:logit_aic_bg}), adjusted McFadden's pseudo $R^2$ values for the 
logistic full models vary between a minimum value of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)` 
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partycode']]` 
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)`
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partycode']]`
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`). 
  

```{r echo=FALSE, warning=FALSE, message=FALSE}

names(logit_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

logit_aic %>% 
  kable(caption = "Akaike Information Criterion values for logistic full and null models 
        \\label{table:logit_aic_bg}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position')) %>% 
  footnote(symbol = 'AIC value refers to Model 11b (constrained).',
           threeparttable = T,
           footnote_as_chunk = T)
```

```{r, results='asis', echo=F}

stargazer::stargazer(finalmod_lst$OLS, 
                     title = "Propensity to vote for a relevant party according to respondents' 
                     socio-demographic characteristics (OLS regression models)",
                     label = 'table:full_ols_cy',
                     type = 'latex',
                     column.labels = c('501', '502', '503', '504','505', '507'),
                     dep.var.labels.include = F,
                     star.cutoffs = c(0.05, 0.01, 0.001),
                     omit.stat=c("f", "ser"),
                     header = F,
                     style = 'ajps')

logit_regtab <- 
  stargazer::stargazer(finalmod_lst$logit, 
                       title = "Vote choice for a relevant party according to respondents' 
                       socio-demographic characteristics (Logistic regression models)",
                       label = 'table:full_logit_cy',
                       type = 'latex',
                       column.labels = c('501', '502', '503', '504','505','505', '507'),
                       dep.var.labels.include = F,
                       star.cutoffs = c(0.05, 0.01, 0.001),
                       omit.stat=c("f", "ser"),
                       header = F,
                       style = 'ajps') %>% 
  capture.output() 

logit_regtab[9] %<>%
  gsub('Model 7', 'Model 12',.) %>% 
  gsub('Model 1$', 'Model 7',.) %>% 
  gsub('Model 6', 'Model 11b',.) %>% 
  gsub('Model 5', 'Model 11a',.) %>% 
  gsub('Model 4', 'Model 10',.) %>% 
  gsub('Model 3', 'Model 9',.) %>% 
  gsub('Model 2', 'Model 8',.) 

cat(logit_regtab, sep = "\n")
  

```


```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = 'NA')

tabs[[1]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 302 and respondents' area of residency 
                   \\label{table:crosstab_1_bg}", booktabs = F) %>%  #  align = c('l', 'c', rep('r',3))
  kable_styling(latex_options = c('striped'))

tabs[[2]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 303 and respondents' subjective social class
                   \\label{table:crosstab_2_bg}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs[[3]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 306 and respondents' education 
                   \\label{table:crosstab_3_bg}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs[[4]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 307 and respondents' subjective social class
                   \\label{table:crosstab_4_bg}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs[[5]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 307 and respondents' subjective social class
                   \\label{table:crosstab_4_bg}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))


```





\newpage
# Cyprus

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Source the Cypriot synteval script # - - - - - - - - - - - - - - - - - - - - - - - - - #

source(here('Scripts', 'synteval_scripts', 'country_spec_scripts', 'EES2019_cy_synteval.R'))

```

Synthetic variables have been estimated for the full set of Cypriot parties available in the original 
2019 EES Cypriot voter study selected according to the criteria stated in the EES 2019 SDM codebook (
for the criteria see Sect. XXX; for the relevant parties see Table \ref{table:relprty_tab_cy}). 

```{r echo=FALSE, warning=FALSE, message=FALSE}
options(knitr.kable.NA = 'NA')
options(knitr.table.format = "latex")

names(relprty_df) <- c('Dep. Var.', 'Party', 'Party name (eng)')

relprty_df %>% 
  kable(caption = "Cypriot relevant parties \\label{table:relprty_tab_cy}", booktabs = T, 
        align = c('l', 'c', 'l')) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

Full OLS models converge and coefficients do not show any particular issue (see Table 
\ref{table:full_ols_cy}). 
In terms of model fit, the adjusted coefficient of determination ($R^2$) values vary between 
a minimum value of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['Adj_Rsq']]` 
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partycode']]` 
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['Adj_Rsq']]`
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partycode']]`
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for full OLS models and null 
models shows that in 4 cases out of 6 null models perform better than full ones (see Table 
\ref{table:ols_aic_cy}).

```{r echo=FALSE, warning=FALSE, message=FALSE}


names(ols_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

ols_aic %>% 
  kable(caption = "Akaike Information Criterion values for OLS full and null models 
        \\label{table:ols_aic_cy}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))


```

On the contrary, three out of six logistic regression models (see Table \ref{table:full_logit_cy}) show 
inflated standard errors for some of the coefficients of interest, in particular: 

* Model 9: D7_rec (only for category 2);
* Model 11a: D8_rec, D5_rec, EDU_rec, D7_rec (only for category 2), D6_une;
* Model 12: D6_une.

Nevertheless, models 9 and 12 constant terms and other regression coefficients are not affected by said 
inflated standard errors, whereas model 5a presents a more problematic profile. 

Model 5a inflated standard errors are due to separation issues. In short, no respondents from rural areas
or small cities, single, low educated, with high subjective socioeconomic status (SES), members of trade 
unions, and unemployed did vote for party 505 (see Tables \ref{table:crosstab_1_cy}, 
\ref{table:crosstab_2_cy}, \ref{table:crosstab_3_cy}, \ref{table:crosstab_4_cy}, 
\ref{table:crosstab_5_cy}, \ref{table:crosstab_6_cy}). 

As a consequence, a constrained version of model 11 (namely, Model 11b) without said variables was 
estimated and contrasted with the original (Model 11a), full model. Likelihood-ratio test results show 
that $H_0$ (namely, that the constrained model fits better than the full model) cannot be rejected 
(see Table \ref{table:lrtest_1_cy}). Consequently, synthetic variables for respondents' vote choice for 
party 505 have been predicted relying on the constrained model (Model 11b). 

```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = '')

anova_lst[[1]] %>%
  kable(caption = "Likelihood-ratio Test between Model 5a (Unconstrained) and Model 5b (Constrained)
                  \\label{table:lrtest_1_cy}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

In terms of model fit, adjusted McFadden's pseudo $R^2$ values for the logistic full models vary between 
a minimum value of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)` 
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partycode']]` 
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)`
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partycode']]`
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for logistic full models and 
null models shows that in 3 cases out of 6 null models perform better than full ones. According to AIC 
values the related null model appears to have a better fit than Model 11b (see Table
\ref{table:logit_aic_cy}). 

```{r echo=FALSE, warning=FALSE, message=FALSE}

logit_aic[6,1] <- 'stack_505*'

names(logit_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

logit_aic %>% 
  kable(caption = "Akaike Information Criterion values for logistic full and null models 
        \\label{table:logit_aic_cy}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position')) %>% 
  footnote(symbol = 'AIC value refers to Model 11b (constrained).',
           threeparttable = T,
           footnote_as_chunk = T)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = 'NA')

tabs[[1]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 505 and respondents' area of residency 
                   \\label{table:crosstab_1_cy}", booktabs = F) %>%  #  align = c('l', 'c', rep('r',3))
  kable_styling(latex_options = c('striped'))

tabs[[2]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 505 and respondents' marital status
                   \\label{table:crosstab_2_cy}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs[[3]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 505 and respondents' education 
                   \\label{table:crosstab_3_cy}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs[[4]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 505 and respondents' subjective SES 
                   \\label{table:crosstab_4_cy}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs[[5]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 505 and respondents' trade union 
                   membership \\label{table:crosstab_5_cy}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs[[6]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 505 and respondents' employment status 
                  \\label{table:crosstab_6_cy}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

```


```{r, results='asis', echo=F}

stargazer::stargazer(finalmod_lst$OLS, 
                     title = "Propensity to vote for a relevant party according to respondents' 
                     socio-demographic characteristics (OLS regression models)",
                     label = 'table:full_ols_cy',
                     type = 'latex',
                     column.labels = c('501', '502', '503', '504','505', '507'),
                     dep.var.labels.include = F,
                     star.cutoffs = c(0.05, 0.01, 0.001),
                     omit.stat=c("f", "ser"),
                     header = F,
                     style = 'ajps')

logit_regtab <- 
  stargazer::stargazer(finalmod_lst$logit, 
                       title = "Vote choice for a relevant party according to respondents' 
                       socio-demographic characteristics (Logistic regression models)",
                       label = 'table:full_logit_cy',
                       type = 'latex',
                       column.labels = c('501', '502', '503', '504','505','505', '507'),
                       dep.var.labels.include = F,
                       star.cutoffs = c(0.05, 0.01, 0.001),
                       omit.stat=c("f", "ser"),
                       header = F,
                       style = 'ajps') %>% 
  capture.output() 

logit_regtab[9] %<>%
  gsub('Model 7', 'Model 12',.) %>% 
  gsub('Model 1$', 'Model 7',.) %>% 
  gsub('Model 6', 'Model 11b',.) %>% 
  gsub('Model 5', 'Model 11a',.) %>% 
  gsub('Model 4', 'Model 10',.) %>% 
  gsub('Model 3', 'Model 9',.) %>% 
  gsub('Model 2', 'Model 8',.) 

cat(logit_regtab, sep = "\n")
  

```






\newpage
# italy

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Source the Cypriot synteval script # - - - - - - - - - - - - - - - - - - - - - - - - - #

source(here('Scripts', 'synteval_scripts', 'country_spec_scripts', 'EES2019_it_synteval.R'))

```

Synthetic variables have been estimated for the full set of relevant parties available in the original 
2019 EES ITalian voter study selected according to the criteria stated in the EES 2019 SDM codebook (
for the criteria see Sect. XXX; for the relevant parties see Table \ref{table:relprty_tab_it}). 

```{r echo=FALSE, warning=FALSE, message=FALSE}
options(knitr.kable.NA = 'NA')
options(knitr.table.format = "latex")

names(relprty_df) <- c('Dep. Var.', 'Party', 'Party name (eng)')

relprty_df %>% 
  kable(caption = "Italian relevant parties \\label{table:relprty_tab_it}", booktabs = T, 
        align = c('l', 'c', 'l')) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```


Full OLS models converge and coefficients do not show any particular issue (see Table 
\ref{table:full_ols_it}). 
In terms of model fit, the adjusted coefficient of determination ($R^2$) values vary between 
a minimum value of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['Adj_Rsq']]` 
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partycode']]` 
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['Adj_Rsq']]`
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partycode']]`
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for full OLS models and null 
models shows in no cases the null models perform better than full ones (see Table 
\ref{table:ols_aic_it}).

```{r echo=FALSE, warning=FALSE, message=FALSE}


names(ols_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

ols_aic %>% 
  kable(caption = "Akaike Information Criterion values for OLS full and null models 
        \\label{table:ols_aic_it}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))


```

Also considering logistic regression models no anomalies were detected. (see Table 
\ref{table:full_logit_it}) In terms of model fit, adjusted McFadden's pseudo $R^2$ values for the 
logistic full models vary between a minimum value of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)` 
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partycode']]` 
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)`
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partycode']]`
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`). 
The differences between Akaike Information Criterion (AIC) values for logistic full models and 
null models shows that in 5 cases out of 7 null models perform marginally better than full ones (see 
Table \ref{table:logit_aic_it}). 

```{r echo=FALSE, warning=FALSE, message=FALSE}

names(logit_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

logit_aic %>% 
  kable(caption = "Akaike Information Criterion values for logistic full and null models 
        \\label{table:logit_aic_it}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position')) %>% 
  footnote(symbol = 'AIC value refers to Model 11b (constrained).',
           threeparttable = T,
           footnote_as_chunk = T)
```

```{r, results='asis', echo=F}

stargazer::stargazer(finalmod_lst$OLS, 
                     title = "Propensity to vote for a relevant party according to respondents' 
                     socio-demographic characteristics (OLS regression models)",
                     label = 'table:full_ols_it',
                     type = 'latex',
                     column.labels = c('1501', '1502', '1503', '1504','1505','1506', '1507'),
                     dep.var.labels.include = F,
                     star.cutoffs = c(0.05, 0.01, 0.001),
                     omit.stat=c("f", "ser"),
                     header = F,
                     style = 'ajps')

logit_regtab <- 
  stargazer::stargazer(finalmod_lst$logit, 
                       title = "Vote choice for a relevant party according to respondents' 
                       socio-demographic characteristics (Logistic regression models)",
                       label = 'table:full_logit_it',
                       type = 'latex',
                       column.labels = c('1501', '1502', '1503', '1504','1505','1506', '1507'),
                       dep.var.labels.include = F,
                       star.cutoffs = c(0.05, 0.01, 0.001),
                       omit.stat=c("f", "ser"),
                       header = F,
                       style = 'ajps') %>% 
  capture.output() 

logit_regtab[9] %<>%
  gsub('Model 1', 'Model 8',.) %>% 
  gsub('Model 2', 'Model 9',.) %>% 
  gsub('Model 3', 'Model 10',.) %>% 
  gsub('Model 4', 'Model 11',.) %>% 
  gsub('Model 5', 'Model 12',.) %>% 
  gsub('Model 6', 'Model 13',.) %>% 
  gsub('Model 7', 'Model 14',.) 

cat(logit_regtab, sep = "\n")
```
