---
title: Summary of Synthetic Variables Estimation 
subtitle: EES 2019 Voter Study (Austrian, Croatian, French, Irish, Latvian, Portugues, Romanian and Slovenian samples)
author: Matthias Körnig
date: 05.04.2022 
toc: false
output: 
  bookdown::pdf_document2:
    includes:
      in_header: eval_header.tex
urlcolor: RedOrange
---

```{r echo=FALSE, warning=FALSE, message=FALSE}

# Load 'here' for sourcing # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
library('here')

# Source the general workflow # - - - - - - - - - - - - - - - - - - - - - - - - - - - - -#
source(here('Scripts', 'synteval', 'Synteval_gen.R'))

```

\newpage
# Austria

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Source the Austrain synteval script # - - - - - - - - - - - - - - - - - - - - - - - - - #

source(here('Scripts', 'synteval', 'country_spec_scripts', 'EES2019_at_synteval.R'))

```

Synthetic variables have been estimated for the full set of Austrain parties available in the original 
2019 EES Austrian voter study selected according to the criteria stated in the EES 2019 SDM codebook (
for the criteria see Sect. XXX; for the relevant parties see Table \ref{table:relprty_tab_at}). 

```{r echo=FALSE, warning=FALSE, message=FALSE}
options(knitr.kable.NA = 'NA')
options(knitr.table.format = "latex")

names(relprty_df) <- c('Dep. Var.', 'Party', 'Party name (eng)')

relprty_df %>% 
  kable(caption = "Austrian relevant parties \\label{table:relprty_tab_at}", booktabs = T, 
        align = c('l', 'c', 'l')) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

Full OLS models converge and coefficients do not show any particular issue (see Table 
\ref{table:full_ols_at}). 
In terms of model fit, the adjusted coefficient of determination ($R^2$) values vary between 
a minimum value of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['Adj_Rsq']]` 
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partycode']]` 
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['Adj_Rsq']]`
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partycode']]`
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for full OLS models and null 
models shows that in all 6 cases out of 6 null models perform better than full ones (see Table 
\ref{table:ols_aic_at}).

```{r echo=FALSE, warning=FALSE, message=FALSE}


names(ols_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

ols_aic %>% 
  kable(caption = "Akaike Information Criterion values for OLS full and null models 
        \\label{table:ols_aic_at}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))


```

On the contrary, one out of six logistic regression models (see Table \ref{table:full_logit_at}) show 
inflated standard errors for some of the coefficients of interest: 

* Model 12: D8_rec, D1_rec;

Model 12 presents more problematic profile, since it affects the models constant terms with its inflated standard errors

Model 12 inflated standard errors are due to separation issues. In short, no respondents from rural areas
or small cities and members of trade unions did vote for party 505 (see Tables \ref{table:crosstab_1_at}, 
\ref{table:crosstab_2_at}). 

As a consequence, a constrained version of model 6 without said variables was 
estimated and contrasted with the original, full model. Likelihood-ratio test results show 
that $H_0$ (namely, that the constrained model does not fit better than the full model) can be rejected at p<0.001
(see Table \ref{table:lrtest_1_at}). Consequently, synthetic variables for respondents' vote choice for 
party 105 have been predicted relying on the unconstrained model. 

```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = '')

anova_lst[[1]] %>%
  kable(caption = "Likelihood-ratio Test between Model 6a (Unconstrained) and Model 6b (Constrained)
                  \\label{table:lrtest_1_at}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

In terms of model fit, adjusted McFadden's pseudo $R^2$ values for the logistic full models vary between 
a minimum value of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)` 
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partycode']]` 
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)`
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partycode']]`
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for logistic full models and 
null models shows that in 5 cases out of 6 null models perform better than full ones.

```{r echo=FALSE, warning=FALSE, message=FALSE}

logit_aic[6,1] <- 'stack_105*'

names(logit_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

logit_aic %>% 
  kable(caption = "Akaike Information Criterion values for logistic full and null models 
        \\label{table:logit_aic_cy}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position')) %>% 
  footnote(symbol = 'AIC value refers to Model 6b (constrained).',
           threeparttable = T,
           footnote_as_chunk = T)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = 'NA')

tabs[[1]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 105 and respondents' area of residency 
                   \\label{table:crosstab_1_at}", booktabs = F) %>%  #  align = c('l', 'c', rep('r',3))
  kable_styling(latex_options = c('striped'))

tabs[[2]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 105 and respondents' marital status
                   \\label{table:crosstab_2_at}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))


```


```{r, results='asis', echo=F}

stargazer::stargazer(finalmod_lst$OLS, 
                     title = "Propensity to vote for a relevant party according to respondents' 
                     socio-demographic characteristics (OLS regression models)",
                     label = 'table:full_ols_at',
                     type = 'latex',
                     column.labels = c('101', '102', '104', '106','103', '105'),
                     dep.var.labels.include = F,
                     star.cutoffs = c(0.05, 0.01, 0.001),
                     omit.stat=c("f", "ser"),
                     header = F,
                     style = 'ajps')

logit_regtab <- 
  stargazer::stargazer(finalmod_lst$logit, 
                       title = "Vote choice for a relevant party according to respondents' 
                       socio-demographic characteristics (Logistic regression models)",
                       label = 'table:full_logit_at',
                       type = 'latex',
                       column.labels = c('101', '102', '104', '106','103', '105'),
                       dep.var.labels.include = F,
                       star.cutoffs = c(0.05, 0.01, 0.001),
                       omit.stat=c("f", "ser"),
                       header = F,
                       style = 'ajps') %>% 
  capture.output() 

logit_regtab[9] %<>%
  gsub('Model 1', 'Model 7',.) %>%
  gsub('Model 6', 'Model 12',.) %>% 
  gsub('Model 5', 'Model 11',.) %>% 
  gsub('Model 4', 'Model 10',.) %>% 
  gsub('Model 3', 'Model 9',.) %>% 
  gsub('Model 2', 'Model 8',.) 

cat(logit_regtab, sep = "\n")
  

```



\newpage
# Croatia

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Source the Croatian synteval script # - - - - - - - - - - - - - - - - - - - - - - - - - #

source(here('Scripts', 'synteval', 'country_spec_scripts', 'EES2019_hr_synteval.R'))

```

Synthetic variables have been estimated for the full set of Croatian parties available in the original 
2019 EES Croatian voter study selected according to the criteria stated in the EES 2019 SDM codebook (
for the criteria see Sect. XXX; for the relevant parties see Table \ref{table:relprty_tab_hr}). 

```{r echo=FALSE, warning=FALSE, message=FALSE}
options(knitr.kable.NA = 'NA')
options(knitr.table.format = "latex")

names(relprty_df) <- c('Dep. Var.', 'Party', 'Party name (eng)')

relprty_df %>% 
  kable(caption = "Croatian relevant parties \\label{table:relprty_tab_hr}", booktabs = T, 
        align = c('l', 'c', 'l')) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

Full OLS models converge and coefficients do not show any particular issue (see Table 
\ref{table:full_ols_hr}). 
In terms of model fit, the adjusted coefficient of determination ($R^2$) values vary between 
a minimum value of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['Adj_Rsq']]` 
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partycode']]` 
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['Adj_Rsq']]`
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partycode']]`
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for full OLS models and null 
models shows that in all 7 cases out of 7 null models perform better than full ones (see Table 
\ref{table:ols_aic_hr}).

```{r echo=FALSE, warning=FALSE, message=FALSE}


names(ols_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

ols_aic %>% 
  kable(caption = "Akaike Information Criterion values for OLS full and null models 
        \\label{table:ols_aic_hr}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))


```

On the contrary, two out of seven logistic regression models (see Table \ref{table:full_logit_hr}) show 
inflated standard errors for some of the coefficients of interest, in particular: 

* Model 8a: D8_rec, D5_rec, EDU_rec, D7_rec (only for category 2), D6_une;
* Model 13a: EDU_rec, D6_une;

Those models 14a and 13a present more problematic profiles, since they affect its models constant terms through their inflated standard errors.

Model 8a and 13a inflated standard errors are due to separation issues. In short, no respondents with low education and in unemployment 
did vote for party 413 (see Tables \ref{table:crosstab_1_hr}, \ref{table:crosstab_2_hr}). As well as no respondents from rural areas
or small cities, single, low educated, with high subjective socioeconomic status (SES) and unemployed did vote for party 401 (see Tables \ref{table:crosstab_3_hr}, \ref{table:crosstab_4_hr}, \ref{table:crosstab_5_hr}, \ref{table:crosstab_6_hr}, \ref{table:crosstab_7_hr}). 

As a consequence, a constrained version of model 8 and 13 (namely, Model 14b, 13b) without said variables was 
estimated and contrasted with the original (Model 14a, 13a), full model. Likelihood-ratio test results show 
that $H_0$ (namely, that the constrained model fits better than the full model)  can be rejected at p<0.1 for 
party 401 (see Table \ref{table:lrtest_1_hr}). For party 413 $H_0$ cannot be rejected (see Table \ref{table:lrtest_2_hr}) Consequently, synthetic variables 
for respondents' vote choice for party 401 and 413 have been predicted relying on the constrained model (Model 14b, 13b). 

```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = '')

anova_lst[[2]] %>%
  kable(caption = "Likelihood-ratio Test between Model 14a (Unconstrained) and Model 8b (Constrained)
                  \\label{table:lrtest_1_hr}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

anova_lst[[1]] %>%
  kable(caption = "Likelihood-ratio Test between Model 13a (Unconstrained) and Model 13b (Constrained)
                  \\label{table:lrtest_2_hr}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

In terms of model fit, adjusted McFadden's pseudo $R^2$ values for the logistic full models vary between 
a minimum value of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)` 
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partycode']]` 
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)`
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partycode']]`
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for logistic full models and 
null models shows that in 3 cases out of 7 null models perform better than full ones. According to AIC 
values the related null models appear to have a better fit than Model 13b and 14b (see Table
\ref{table:logit_aic_hr}). 

```{r echo=FALSE, warning=FALSE, message=FALSE}

logit_aic[2,1] <- 'stack_401*'
logit_aic[8,1] <- 'stack_413*'

names(logit_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

logit_aic %>% 
  kable(caption = "Akaike Information Criterion values for logistic full and null models 
        \\label{table:logit_aic_hr}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position')) %>% 
  footnote(symbol = 'AIC value refers to Model 13b and 14b (constrained).',
           threeparttable = T,
           footnote_as_chunk = T)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = 'NA')

tabs[[1]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 413 and respondents' education 
                   \\label{table:crosstab_1_hr}", booktabs = F) %>%  #  align = c('l', 'c', rep('r',3))
  kable_styling(latex_options = c('striped'))

tabs[[2]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 413 and respondents' employment status
                   \\label{table:crosstab_2_hr}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs2[[1]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 401 and respondents' education
                   \\label{table:crosstab_3_hr}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs2[[2]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 401 and respondents' employment status 
                   \\label{table:crosstab_4_hr}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs2[[3]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 401 and respondents' subjective SES
                   membership \\label{table:crosstab_5_hr}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs2[[4]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 401 and respondents' marital status
                  \\label{table:crosstab_6_hr}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs2[[5]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 401 and respondents' area of residency 
                  \\label{table:crosstab_7_hr}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

```


```{r, results='asis', echo=F}

stargazer::stargazer(finalmod_lst$OLS, 
                     title = "Propensity to vote for a relevant party according to respondents' 
                     socio-demographic characteristics (OLS regression models)",
                     label = 'table:full_ols_hr',
                     type = 'latex',
                     column.labels = c('412', '404', '414', '405','406', '413', '401'),
                     dep.var.labels.include = F,
                     star.cutoffs = c(0.05, 0.01, 0.001),
                     omit.stat=c("f", "ser"),
                     header = F,
                     style = 'ajps')

logit_regtab <- 
  stargazer::stargazer(finalmod_lst$logit, 
                       title = "Vote choice for a relevant party according to respondents' 
                       socio-demographic characteristics (Logistic regression models)",
                       label = 'table:full_logit_hr',
                       type = 'latex',
                       no.space = T, # to remove the spaces after each line of coefficients
                       column.sep.width = '0.5pt', # to reduce column width
                       font.size = 'footnotesize', # to make font size smaller
                       column.labels = c('412', '404', '414', '405','406', '413',  '413', '401', '401'),
                       dep.var.labels.include = F,
                       star.cutoffs = c(0.05, 0.01, 0.001),
                       omit.stat=c("f", "ser"),
                       header = F,
                       style = 'ajps') %>% 
  capture.output() 

logit_regtab[9] %<>%
  gsub('Model 9', 'Model 14b',.) %>%
  gsub('Model 8', 'Model 14a',.) %>%
  gsub('Model 7', 'Model 13b',.) %>% 
  gsub('Model 1$', 'Model 8',.) %>% 
  gsub('Model 6', 'Model 13a',.) %>% 
  gsub('Model 5', 'Model 12',.) %>% 
  gsub('Model 4', 'Model 11',.) %>% 
  gsub('Model 3', 'Model 10',.) %>% 
  gsub('Model 2', 'Model 9',.) 
  

cat(logit_regtab, sep = "\n")
  

```



\newpage
# France

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Source the French synteval script # - - - - - - - - - - - - - - - - - - - - - - - - - #

source(here('Scripts', 'synteval', 'country_spec_scripts', 'EES2019_fr_synteval.R'))

```

Synthetic variables have been estimated for the full set of French parties available in the original 
2019 EES French voter study selected according to the criteria stated in the EES 2019 SDM codebook (
for the criteria see Sect. XXX; for the relevant parties see Table \ref{table:relprty_tab_fr}). 

```{r echo=FALSE, warning=FALSE, message=FALSE}
options(knitr.kable.NA = 'NA')
options(knitr.table.format = "latex")

names(relprty_df) <- c('Dep. Var.', 'Party', 'Party name (eng)')

relprty_df %>% 
  kable(caption = "French relevant parties \\label{table:relprty_tab_fr}", booktabs = T, 
        align = c('l', 'c', 'l')) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

Full OLS models converge and coefficients do not show any particular issue (see Table 
\ref{table:full_ols_fr}). 
In terms of model fit, the adjusted coefficient of determination ($R^2$) values vary between 
a minimum value of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['Adj_Rsq']]` 
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partycode']]` 
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['Adj_Rsq']]`
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partycode']]`
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for full OLS models and null 
models shows that in 7 cases out of 7 null models perform better than full ones (see Table 
\ref{table:ols_aic_fr}).

```{r echo=FALSE, warning=FALSE, message=FALSE}


names(ols_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

ols_aic %>% 
  kable(caption = "Akaike Information Criterion values for OLS full and null models 
        \\label{table:ols_aic_fr}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))


```

Also the full Logit models converge and coefficients do not show any particular issue (see Table \ref{table:full_logit_fr}) 
In terms of model fit, adjusted McFadden's pseudo $R^2$ values for the logistic full models vary between 
a minimum value of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)` 
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partycode']]` 
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)`
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partycode']]`
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for logistic full models and 
null models shows that in 2 cases out of 6 null models perform better than full ones.

```{r echo=FALSE, warning=FALSE, message=FALSE}

names(logit_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

logit_aic %>% 
  kable(caption = "Akaike Information Criterion values for logistic full and null models 
        \\label{table:logit_aic_fr}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position')) 
  
```



```{r, results='asis', echo=F}

stargazer::stargazer(finalmod_lst$OLS, 
                     title = "Propensity to vote for a relevant party according to respondents' 
                     socio-demographic characteristics (OLS regression models)",
                     label = 'table:full_ols_fr',
                     type = 'latex',
                     column.labels = c('1113', '1105', '1111', '1114','1101', '1110', '1102'),
                     dep.var.labels.include = F,
                     star.cutoffs = c(0.05, 0.01, 0.001),
                     omit.stat=c("f", "ser"),
                     header = F,
                     style = 'ajps')

logit_regtab <- 
  stargazer::stargazer(finalmod_lst$logit, 
                       title = "Vote choice for a relevant party according to respondents' 
                       socio-demographic characteristics (Logistic regression models)",
                       label = 'table:full_logit_fr',
                       type = 'latex',
                       column.labels = c('1113', '1105', '1111', '1114','1101', '1110', '1102'),
                       dep.var.labels.include = F,
                       star.cutoffs = c(0.05, 0.01, 0.001),
                       omit.stat=c("f", "ser"),
                       header = F,
                       style = 'ajps') %>% 
  capture.output() 

logit_regtab[9] %<>%
  gsub('Model 1', 'Model 8',.) %>%
  gsub('Model 7', 'Model 14',.) %>% 
  gsub('Model 6', 'Model 13',.) %>% 
  gsub('Model 5', 'Model 12',.) %>% 
  gsub('Model 4', 'Model 11',.) %>% 
  gsub('Model 3', 'Model 10',.) %>% 
  gsub('Model 2', 'Model 9',.) 

cat(logit_regtab, sep = "\n")
  

```

\newpage
\newpage
# Ireland

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Source the Irish synteval script # - - - - - - - - - - - - - - - - - - - - - - - - - #

source(here('Scripts', 'synteval', 'country_spec_scripts', 'EES2019_ie_synteval.R'))

```

Synthetic variables have been estimated for the full set of Irish parties available in the original 
2019 EES Irish voter study selected according to the criteria stated in the EES 2019 SDM codebook (
for the criteria see Sect. XXX; for the relevant parties see Table \ref{table:relprty_tab_ie}). 

```{r echo=FALSE, warning=FALSE, message=FALSE}
options(knitr.kable.NA = 'NA')
options(knitr.table.format = "latex")

names(relprty_df) <- c('Dep. Var.', 'Party', 'Party name (eng)')

relprty_df %>% 
  kable(caption = "Irish relevant parties \\label{table:relprty_tab_ie}", booktabs = T, 
        align = c('l', 'c', 'l')) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

Full OLS models converge and coefficients do not show any particular issue (see Table 
\ref{table:full_ols_ie}). 
In terms of model fit, the adjusted coefficient of determination ($R^2$) values vary between 
a minimum value of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['Adj_Rsq']]` 
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partycode']]` 
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['Adj_Rsq']]`
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partycode']]`
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for full OLS models and null 
models shows that in 6 cases out of 6 null models perform better than full ones (see Table 
\ref{table:ols_aic_ie}).

```{r echo=FALSE, warning=FALSE, message=FALSE}


names(ols_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

ols_aic %>% 
  kable(caption = "Akaike Information Criterion values for OLS full and null models 
        \\label{table:ols_aic_ie}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))


```

On the contrary, one out of six logistic regression models (see Table \ref{table:full_logit_ie}) shows 
inflated standard errors for one of the coefficients of interest: 

* Model 8: EDU_rec;

It presents a problematic profile since the inflated standard error is affecting the constant term.

Model 8a inflated standard errors are due to separation issues. In short, only one low educated 
respondent did vote for party 1403 (see Tables \ref{table:crosstab_1_ie})

As a consequence, a constrained version of model 8 (namely, Model 8b) without said variables was 
estimated and contrasted with the original (Model 8a), full model. Likelihood-ratio test results show 
that $H_0$ (namely, that the constrained model fits better than the full model) cannot be rejected 
(see Table \ref{table:lrtest_1_ie}). Consequently, synthetic variables for respondents' vote choice for 
party 1403 have been predicted relying on the constrained model (Model 8b). 

```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = '')

anova_lst[[1]] %>%
  kable(caption = "Likelihood-ratio Test between Model 8a (Unconstrained) and Model 8b (Constrained)
                  \\label{table:lrtest_1_ie}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

In terms of model fit, adjusted McFadden's pseudo $R^2$ values for the logistic full models vary between 
a minimum value of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)` 
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partycode']]` 
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)`
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partycode']]`
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for logistic full models and 
null models shows that in 4 cases out of 6 null models perform better than full ones. According to AIC 
values the related null model appears to have a better fit than Model 8b (see Table
\ref{table:logit_aic_ie}). 

```{r echo=FALSE, warning=FALSE, message=FALSE}

logit_aic[4,1] <- 'stack_1403*'

names(logit_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

logit_aic %>% 
  kable(caption = "Akaike Information Criterion values for logistic full and null models 
        \\label{table:logit_aic_ie}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position')) %>% 
  footnote(symbol = 'AIC value refers to Model 8b (constrained).',
           threeparttable = T,
           footnote_as_chunk = T)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = 'NA')

tabs[[1]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 505 and respondents' education 
                   \\label{table:crosstab_1_ie}", booktabs = F) %>%  #  align = c('l', 'c', rep('r',3))
  kable_styling(latex_options = c('striped'))

```


```{r, results='asis', echo=F}

stargazer::stargazer(finalmod_lst$OLS, 
                     title = "Propensity to vote for a relevant party according to respondents' 
                     socio-demographic characteristics (OLS regression models)",
                     label = 'table:full_ols_ie',
                     type = 'latex',
                     column.labels = c('1402', '1403', '1401', '1404','1405', '1406'),
                     dep.var.labels.include = F,
                     star.cutoffs = c(0.05, 0.01, 0.001),
                     omit.stat=c("f", "ser"),
                     header = F,
                     style = 'ajps')

logit_regtab <- 
  stargazer::stargazer(finalmod_lst$logit, 
                       title = "Vote choice for a relevant party according to respondents' 
                       socio-demographic characteristics (Logistic regression models)",
                       label = 'table:full_logit_ie',
                       type = 'latex',
                       column.labels = c('1402', '1403', '1403', '1401', '1404','1405', '1406'),
                       dep.var.labels.include = F,
                       star.cutoffs = c(0.05, 0.01, 0.001),
                       omit.stat=c("f", "ser"),
                       header = F,
                       style = 'ajps') %>% 
  capture.output() 

logit_regtab[9] %<>%
  gsub('Model 7', 'Model 12',.) %>% 
  gsub('Model 1$', 'Model 7',.) %>% 
  gsub('Model 6', 'Model 11',.) %>% 
  gsub('Model 5', 'Model 10',.) %>% 
  gsub('Model 4', 'Model 9',.) %>% 
  gsub('Model 3', 'Model 8b',.) %>% 
  gsub('Model 2', 'Model 8a',.) 

cat(logit_regtab, sep = "\n")
  

```



\newpage
# Latvia

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Source the Latvian synteval script # - - - - - - - - - - - - - - - - - - - - - - - - - #

source(here('Scripts', 'synteval', 'country_spec_scripts', 'EES2019_lv_synteval.R'))

```

Synthetic variables have been estimated for the full set of Latvian parties available in the original 
2019 EES Latvian voter study selected according to the criteria stated in the EES 2019 SDM codebook (
for the criteria see Sect. XXX; for the relevant parties see Table \ref{table:relprty_tab_lv}). 

```{r echo=FALSE, warning=FALSE, message=FALSE}
options(knitr.kable.NA = 'NA')
options(knitr.table.format = "latex")

names(relprty_df) <- c('Dep. Var.', 'Party', 'Party name (eng)')

relprty_df %>% 
  kable(caption = "latvian relevant parties \\label{table:relprty_tab_lv}", booktabs = T, 
        align = c('l', 'c', 'l')) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

Full OLS models converge and coefficients do not show any particular issue (see Table 
\ref{table:full_ols_lv}). 
In terms of model fit, the adjusted coefficient of determination ($R^2$) values vary between 
a minimum value of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['Adj_Rsq']]` 
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partycode']]` 
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['Adj_Rsq']]`
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partycode']]`
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for full OLS models and null 
models shows that in 5 cases out of 7 null models perform better than full ones (see Table 
\ref{table:ols_aic_lv}).

```{r echo=FALSE, warning=FALSE, message=FALSE}


names(ols_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

ols_aic %>% 
  kable(caption = "Akaike Information Criterion values for OLS full and null models 
        \\label{table:ols_aic_lv}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))


```

On the contrary, six out of seven logistic regression models (see Tables \ref{table:full_logit_lv_p1},
\ref{table:full_logit_lv_p2}) show inflated standard errors for some of the coefficients of interest, 
in particular: 

* Model 8,14: EDU_rec, D6_une;
* Model 9: D6_une;
* Model 11: D5_rec;
* Model 12,13: EDU_rec.

Nevertheless, models 9 and 11 constant terms and other regression coefficients are not affected by said 
inflated standard errors, whereas model 8,12,13,14 presents a more problematic profile. 

Models 8,12,13,14 inflated standard errors are due to separation issues. In short, no respondents with low 
education and unemployement did vote for party 1611 and 1616 (see Tables \ref{table:crosstab_1_lv}, 
\ref{table:crosstab_2_lv}, \ref{table:crosstab_3_lv}, \ref{table:crosstab_4_lv}). For party 1610 and 1604
no respondents with low education voted for them (see Tables \ref{table:crosstab_5_lv}, \ref{table:crosstab_6_lv}). 

As a consequence, a constrained version of model 8,12,13,14 (namely, Model 8b,12b,13b,14b) without said variables was 
estimated and contrasted with the original (Model 8a,12a,13a,14a), full model. Likelihood-ratio test results show 

* that for Model 8 $H_0$ (namely, that the constrained model fits better than the full model) can be rejected at p<0.05 (see Table \ref{table:lrtest_1_lv}). However, if just EDU_rec is dropped, $H_0$ can be rejected at p<0.1 and the constant term is also not affected (see Table \ref{table:lrtest_2_lv}). Thus, synthetic variables for respondents' vote choice for party 1611 have been predicted relying on the constrained model dropping only EDU_rec.
* that for Model 12 $H_0$ can be rejected at p<0.1 (see Table \ref{table:lrtest_3_lv}). Consequently, synthetic variables for respondents' vote choice for 
party 1610 have been predicted relying on the constrained model (Model 12b).
* that for Model 13 $H_0$ can be rejected at p<0.05 (see Table \ref{table:lrtest_4_lv}). Consequently, synthetic variables for respondents' vote choice for 
party 1604 have been predicted relying on the constrained model (Model 13b).
* that for Model 14 $H_0$ can be rejected at p<0.001 (see Table \ref{table:lrtest_5_lv}). Consequently, synthetic variables for respondents' vote choice for 
party 1616 have been predicted relying on the unconstrained model (Model 14).


```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = '')

anova_lst2[[1]] %>%
  kable(caption = "Likelihood-ratio Test between Model 8a (Unconstrained) and (Fully Constrained)
                  \\label{table:lrtest_1_lv}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

anova_lst[[1]] %>%
  kable(caption = "Likelihood-ratio Test between Model 8a (Unconstrained) and Model 8b (Constrained)
                  \\label{table:lrtest_2_lv}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

anova_lst[[4]] %>%
  kable(caption = "Likelihood-ratio Test between Model 12a (Unconstrained) and Model 12b (Constrained)
                  \\label{table:lrtest_3_lv}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

anova_lst[[5]] %>%
  kable(caption = "Likelihood-ratio Test between Model 13a (Unconstrained) and Model 13b (Constrained)
                  \\label{table:lrtest_4_lv}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

anova_lst[[6]] %>%
  kable(caption = "Likelihood-ratio Test between Model 14 (Unconstrained and Constrained)
                  \\label{table:lrtest_5_lv}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

In terms of model fit, adjusted McFadden's pseudo $R^2$ values for the logistic full models vary between 
a minimum value of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)` 
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partycode']]` 
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)`
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partycode']]`
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for logistic full models and 
null models shows that in 3 cases out of 7 null models perform better than full ones. According to AIC 
values the related null model appears to have a better fit than Model 11b (see Table
\ref{table:logit_aic_lv}). 

```{r echo=FALSE, warning=FALSE, message=FALSE}

logit_aic[2,1] <- 'stack_1611*'
logit_aic[9,1] <- 'stack_1610*'
logit_aic[11,1] <- 'stack_1604*'

names(logit_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

logit_aic %>% 
  kable(caption = "Akaike Information Criterion values for logistic full and null models 
        \\label{table:logit_aic_lv}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position')) %>% 
  footnote(symbol = 'AIC value refers to Model 11b (constrained).',
           threeparttable = T,
           footnote_as_chunk = T)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = 'NA')

tabs[[1]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 1611 and respondents' education
                   \\label{table:crosstab_1_lv}", booktabs = F) %>%  #  align = c('l', 'c', rep('r',3))
  kable_styling(latex_options = c('striped'))

tabs[[2]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 1611 and respondents' employment status
                   \\label{table:crosstab_2_lv}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs6[[1]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 1616 and respondents' education 
                   \\label{table:crosstab_3_lv}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs6[[2]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 1616 and respondents' employment status
                   \\label{table:crosstab_4_lv}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs4[[1]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 1610 and respondents' education
                   membership \\label{table:crosstab_5_lv}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs5[[1]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 1604 and respondents' education
                  \\label{table:crosstab_6_lv}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

```


```{r, results='asis', echo=F}

stargazer::stargazer(finalmod_lst$OLS, 
                     title = "Propensity to vote for a relevant party according to respondents' 
                     socio-demographic characteristics (OLS regression models)",
                     label = 'table:full_ols_lv',
                     type = 'latex',
                     column.labels = c('1611', '1608', '1609', '1605','1610', '1604', '1616'),
                     dep.var.labels.include = F,
                     star.cutoffs = c(0.05, 0.01, 0.001),
                     omit.stat=c("f", "ser"),
                     header = F,
                     style = 'ajps')


finalmod_lst2 <- finalmod_lst[["logit"]][-c(6,7,8,9,10)]
finalmod_lst3 <- finalmod_lst[["logit"]][-c(1,2,3,4,5)]

logit_regtab <- 
  stargazer::stargazer(finalmod_lst2, 
                       title = "Vote choice for a relevant party according to respondents' 
                       socio-demographic characteristics (Logistic regression models)",
                       label = 'table:full_logit_lv_p1',
                       type = 'latex',
                       column.labels = c('1611', '1611', '1608', '1609', '1605'),
                       dep.var.labels.include = F,
                       star.cutoffs = c(0.05, 0.01, 0.001),
                       omit.stat=c("f", "ser"),
                       header = F,
                       style = 'ajps') %>% 
  capture.output() 

logit_regtab2 <- 
  stargazer::stargazer(finalmod_lst3, 
                       title = "Vote choice for a relevant party according to respondents' 
                       socio-demographic characteristics (Logistic regression models)",
                       label = 'table:full_logit_lv_p2',
                       type = 'latex',
                       column.labels = c('1610', '1610', '1604', '1604', '1616'),
                       dep.var.labels.include = F,
                       star.cutoffs = c(0.05, 0.01, 0.001),
                       omit.stat=c("f", "ser"),
                       header = F,
                       style = 'ajps') %>% 
  capture.output() 


logit_regtab[9] %<>%
  gsub('Model 1', 'Model 8',.) %>% 
  gsub('Model 2', 'Model 8a',.) %>% 
  gsub('Model 3', 'Model 9',.) %>% 
  gsub('Model 4', 'Model 10',.) %>% 
  gsub('Model 5', 'Model 11',.)

cat(logit_regtab, sep = "\n")

logit_regtab2[9] %<>%
  gsub('Model 1', 'Model 12a',.) %>% 
  gsub('Model 2', 'Model 12b',.) %>% 
  gsub('Model 3', 'Model 13a',.) %>% 
  gsub('Model 4', 'Model 13b',.) %>% 
  gsub('Model 5', 'Model 14',.) 

cat(logit_regtab2, sep = "\n")
  
  

```


\newpage
# Romania

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Source the Romanian synteval script # - - - - - - - - - - - - - - - - - - - - - - - - - #

source(here('Scripts', 'synteval', 'country_spec_scripts', 'EES2019_ro_synteval.R'))

```

Synthetic variables have been estimated for the full set of Romania parties available in the original 
2019 EES Romanian voter study selected according to the criteria stated in the EES 2019 SDM codebook (
for the criteria see Sect. XXX; for the relevant parties see Table \ref{table:relprty_tab_ro}). 

```{r echo=FALSE, warning=FALSE, message=FALSE}
options(knitr.kable.NA = 'NA')
options(knitr.table.format = "latex")

names(relprty_df) <- c('Dep. Var.', 'Party', 'Party name (eng)')

relprty_df %>% 
  kable(caption = "Romanian relevant parties \\label{table:relprty_tab_ro}", booktabs = T, 
        align = c('l', 'c', 'l')) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

Full OLS models converge and coefficients do not show any particular issue (see Table 
\ref{table:full_ols_ro}). 
In terms of model fit, the adjusted coefficient of determination ($R^2$) values vary between 
a minimum value of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['Adj_Rsq']]` 
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partycode']]` 
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['Adj_Rsq']]`
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partycode']]`
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for full OLS models and null 
models shows that in 7 cases out of 7 null models perform better than full ones (see Table 
\ref{table:ols_aic_ro}).

```{r echo=FALSE, warning=FALSE, message=FALSE}


names(ols_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

ols_aic %>% 
  kable(caption = "Akaike Information Criterion values for OLS full and null models 
        \\label{table:ols_aic_ro}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))


```

On the contrary, one out of seven logistic regression models (see Table \ref{table:full_logit_ro}) show 
inflated standard errors for some of the coefficients of interest: 

* Model 12: EDU_rec, D6_une;

It presents a problematic profile since the inflated standard errors affect the constant term.

Model 12a inflated standard errors are due to separation issues. In short, no respondents with low 
education and in unemployment did vote for party 2307 (see Tables \ref{table:crosstab_1_ro}, 
\ref{table:crosstab_2_ro}). 

As a consequence, a constrained version of model 12 (namely, Model 11b) without said variables was 
estimated and contrasted with the original (Model 12a), full model. Likelihood-ratio test results show 
that $H_0$ (namely, that the constrained model fits better than the full model) can be rejected at p<0.001
(see Table \ref{table:lrtest_1_ro}). However, if just EDU_rec is dropped $H_0$ cannot be rejected 
(see Table \ref{table:lrtest_2_ro}). Consequently, synthetic variables for respondents' vote choice for 
party 2307 have been predicted relying on the constrained model where just EDU_rec is dropped (Model 12b). 

```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = '')

anova_lst2[[1]] %>%
  kable(caption = "Likelihood-ratio Test between Model 12a (Unconstrained) and (Fully Constrained)
                  \\label{table:lrtest_1_ro}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

anova_lst[[1]] %>%
  kable(caption = "Likelihood-ratio Test between Model 12a (Unconstrained) and Model 12b (Constrained)
                  \\label{table:lrtest_2_ro}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

In terms of model fit, adjusted McFadden's pseudo $R^2$ values for the logistic full models vary between 
a minimum value of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)` 
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partycode']]` 
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)`
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partycode']]`
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for logistic full models and 
null models shows that in 3 cases out of 7 null models perform better than full ones. According to AIC 
values the related null model appears to have a better fit than Model 12b (see Table
\ref{table:logit_aic_ro}). 

```{r echo=FALSE, warning=FALSE, message=FALSE}

logit_aic[7,1] <- 'stack_2307*'

names(logit_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

logit_aic %>% 
  kable(caption = "Akaike Information Criterion values for logistic full and null models 
        \\label{table:logit_aic_ro}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position')) %>% 
  footnote(symbol = 'AIC value refers to Model 12b (constrained).',
           threeparttable = T,
           footnote_as_chunk = T)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = 'NA')

tabs[[1]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 505 and respondents' education 
                   \\label{table:crosstab_1_ro}", booktabs = F) %>%  #  align = c('l', 'c', rep('r',3))
  kable_styling(latex_options = c('striped'))

tabs[[2]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 505 and respondents' employment
                   \\label{table:crosstab_2_ro}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))


```


```{r, results='asis', echo=F}

stargazer::stargazer(finalmod_lst$OLS, 
                     title = "Propensity to vote for a relevant party according to respondents' 
                     socio-demographic characteristics (OLS regression models)",
                     label = 'table:full_ols_ro',
                     type = 'latex',
                     column.labels = c('2301', '2303', '2305', '2306', '2307', '2308', '2302'),
                     dep.var.labels.include = F,
                     star.cutoffs = c(0.05, 0.01, 0.001),
                     omit.stat=c("f", "ser"),
                     header = F,
                     style = 'ajps')

logit_regtab <- 
  stargazer::stargazer(finalmod_lst$logit, 
                       title = "Vote choice for a relevant party according to respondents' 
                       socio-demographic characteristics (Logistic regression models)",
                       label = 'table:full_logit_ro',
                       type = 'latex',
                       no.space = T, # to remove the spaces after each line of coefficients
                       column.sep.width = '0.5pt', # to reduce column width
                       font.size = 'small', # to make font size smaller
                       column.labels = c('2301', '2303', '2305', '2306', '2307', '2307', '2308', '2302'),
                       dep.var.labels.include = F,
                       star.cutoffs = c(0.05, 0.01, 0.001),
                       omit.stat=c("f", "ser"),
                       header = F,
                       style = 'ajps') %>% 
  capture.output() 

logit_regtab[9] %<>%
  gsub('Model 8', 'Model 14',.) %>% 
  gsub('Model 1$', 'Model 8',.) %>%
  gsub('Model 7', 'Model 13',.) %>%
  gsub('Model 6', 'Model 12b',.) %>% 
  gsub('Model 5', 'Model 12a',.) %>% 
  gsub('Model 4', 'Model 11',.) %>% 
  gsub('Model 3', 'Model 10',.) %>% 
  gsub('Model 2', 'Model 9',.) 

cat(logit_regtab, sep = "\n")
  

```



\newpage
# Slovenia

```{r echo=FALSE, warning=FALSE, message=FALSE}
# Source the Slovenian synteval script # - - - - - - - - - - - - - - - - - - - - - - - - - #

source(here('Scripts', 'synteval', 'country_spec_scripts', 'EES2019_si_synteval.R'))

```

Synthetic variables have been estimated for the full set of Slovenian parties available in the original 
2019 EES Slovenian voter study selected according to the criteria stated in the EES 2019 SDM codebook (
for the criteria see Sect. XXX; for the relevant parties see Table \ref{table:relprty_tab_si}). 

```{r echo=FALSE, warning=FALSE, message=FALSE}
options(knitr.kable.NA = 'NA')
options(knitr.table.format = "latex")

names(relprty_df) <- c('Dep. Var.', 'Party', 'Party name (eng)')

relprty_df %>% 
  kable(caption = "Slovenian relevant parties \\label{table:relprty_tab_si}", booktabs = T, 
        align = c('l', 'c', 'l')) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

Full OLS models converge and coefficients do not show any particular issue (see Table 
\ref{table:full_ols_si}). 
In terms of model fit, the adjusted coefficient of determination ($R^2$) values vary between 
a minimum value of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['Adj_Rsq']]` 
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partycode']]` 
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['Adj_Rsq']]`
for party `r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partycode']]`
(`r ols_df %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for full OLS models and null 
models shows that in 8 cases out of 9 null models perform better than full ones (see Table 
\ref{table:ols_aic_si}).

```{r echo=FALSE, warning=FALSE, message=FALSE}


names(ols_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

ols_aic %>% 
  kable(caption = "Akaike Information Criterion values for OLS full and null models 
        \\label{table:ols_aic_si}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))


```

On the contrary, three out of nine logistic regression models (see Tables \ref{table:full_logit_si_p1},
\ref{table:full_logit_si_p2}) show inflated standard errors for some of the coefficients of interest, 
in particular: 

* Model 14: Edu_rec, D7_rec (category 2 only);
* Model 16: D6_une;
* Model 17: EDU_rec.

Nevertheless, model 16 constant terms and other regression coefficients are not affected by said 
inflated standard errors, whereas models 14a and 17a present a more problematic profile. 

Model 14a inflated standard errors are due to separation issues. In short, no respondents with 
low education and high subjective socioeconomic status (SES) did vote for party 2405 (see Tables \ref{table:crosstab_1_si}, 
\ref{table:crosstab_2_si}). In Model 17a, no respondents with low education did cote for party 2408
(see Table \ref{table:crosstab_3_si}).

As a consequence, a constrained version of model 14 and 17 (namely, Model 14b,17b) without said variables was 
estimated and contrasted with the original (Model 14a,17a), full model. Likelihood-ratio test results show 
that in case of model 14 $H_0$ (namely, that the constrained model fits better than the full model) can be rejected 
at p<0.001 (see Table \ref{table:lrtest_1_si}). However, if just EDU_rec is dropped $H_0$ can be rejected at p<0.1 
(See Table \ref{table:lrtest_2_si}). For model 17 $H_0$ cannot be rejected (see Table \ref{table:lrtest_3_si}). 
Consequently, synthetic variables for respondents' vote choice for party 2405 and 2408 both have been 
predicted relying on the constrained model dropping EDU_rec (Model 14b,17b). 

```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = '')

anova_lst2[[1]] %>%
  kable(caption = "Likelihood-ratio Test between Model 14a (Unconstrained) and (Fully Constrained)
                  \\label{table:lrtest_1_si}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

anova_lst2[[1]] %>%
  kable(caption = "Likelihood-ratio Test between Model 14a (Unconstrained) and Model 14b (Constrained)
                  \\label{table:lrtest_2_si}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

anova_lst[[2]] %>%
  kable(caption = "Likelihood-ratio Test between Model 17a (Unconstrained) and Model 17b (Constrained)
                  \\label{table:lrtest_3_si}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

In terms of model fit, adjusted McFadden's pseudo $R^2$ values for the logistic full models vary between 
a minimum value of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)` 
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partycode']]` 
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of 
`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)`
for party `r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partycode']]`
(`r logit_df %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for logistic full models and 
null models shows that in 5 cases out of 9 null models perform better than full ones. According to AIC 
values the related null model appears to have a better fit than Model 14b and 17b (see Table
\ref{table:logit_aic_si}). 

```{r echo=FALSE, warning=FALSE, message=FALSE}

logit_aic[1,1] <- 'stack_2408*'
logit_aic[7,1] <- 'stack_2405*'

names(logit_aic) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

logit_aic %>% 
  kable(caption = "Akaike Information Criterion values for logistic full and null models 
        \\label{table:logit_aic_si}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position')) %>% 
  footnote(symbol = 'AIC value refers to Model 14b and 17b (constrained).',
           threeparttable = T,
           footnote_as_chunk = T)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = 'NA')

tabs[[1]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 2405 and respondents' education
                   \\label{table:crosstab_1_si}", booktabs = F) %>%  #  align = c('l', 'c', rep('r',3))
  kable_styling(latex_options = c('striped'))

tabs[[2]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 2405 and respondents' subjective SES
                   \\label{table:crosstab_2_si}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs2[[1]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 2408 and respondents' education 
                   \\label{table:crosstab_3_si}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

```


```{r, results='asis', echo=F}

stargazer::stargazer(finalmod_lst$OLS, 
                     title = "Propensity to vote for a relevant party according to respondents' 
                     socio-demographic characteristics (OLS regression models)",
                     label = 'table:full_ols_si',
                     type = 'latex',
                     no.space = T, # to remove the spaces after each line of coefficients
                     column.sep.width = '0.5pt', # to reduce column width
                     font.size = 'footnotesize', # to make font size smaller
                     column.labels = c('2401', '2402', '2403', '2404','2405', '2406', '2407', '2408', '2409'),
                     dep.var.labels.include = F,
                     star.cutoffs = c(0.05, 0.01, 0.001),
                     omit.stat=c("f", "ser"),
                     header = F,
                     style = 'ajps')


finalmod_lst2 <- finalmod_lst[["logit"]][-c(7,8,9,10,11)]
finalmod_lst3 <- finalmod_lst[["logit"]][-c(1,2,3,4,5,6)]

logit_regtab <- 
  stargazer::stargazer(finalmod_lst2, 
                       title = "Vote choice for a relevant party according to respondents' 
                       socio-demographic characteristics (Logistic regression models)",
                       label = 'table:full_logit_si_p1',
                       type = 'latex',
                       column.labels = c('2401', '2402', '2403', '2404', '2405', '2405'),
                       dep.var.labels.include = F,
                       star.cutoffs = c(0.05, 0.01, 0.001),
                       omit.stat=c("f", "ser"),
                       header = F,
                       style = 'ajps') %>% 
  capture.output() 

logit_regtab2 <- 
  stargazer::stargazer(finalmod_lst3, 
                       title = "Vote choice for a relevant party according to respondents' 
                       socio-demographic characteristics (Logistic regression models)",
                       label = 'table:full_logit_si_p2',
                       type = 'latex',
                       column.labels = c('2406', '2407', '2408', '2408', '2409'),
                       dep.var.labels.include = F,
                       star.cutoffs = c(0.05, 0.01, 0.001),
                       omit.stat=c("f", "ser"),
                       header = F,
                       style = 'ajps') %>% 
  capture.output() 


logit_regtab[9] %<>%
  gsub('Model 1', 'Model 10',.) %>% 
  gsub('Model 2', 'Model 11',.) %>% 
  gsub('Model 3', 'Model 12',.) %>% 
  gsub('Model 4', 'Model 13',.) %>% 
  gsub('Model 5', 'Model 14a',.) %>% 
  gsub('Model 6', 'Model 14b',.) 

cat(logit_regtab, sep = "\n")

logit_regtab2[9] %<>%
  gsub('Model 1', 'Model 15',.) %>% 
  gsub('Model 2', 'Model 16',.) %>% 
  gsub('Model 3', 'Model 17a',.) %>% 
  gsub('Model 4', 'Model 17b',.) %>% 
  gsub('Model 5', 'Model 18',.) 

cat(logit_regtab2, sep = "\n")
  

```









