---
title: Summary of Synthetic Variables Estimation 
subtitle: EES 2019 Voter Study (Belgian, Bulgarian, Cypriot, and Italian samples)
author: Giuseppe Carteny
date: 26.10.2021 
toc: false
output: 
  bookdown::pdf_document2:
    includes:
      in_header: eval_header.tex
urlcolor: RedOrange
---

```{r echo=FALSE, warning=FALSE, message=FALSE, }

# Admin # ==============================================================================================

want = c("tidyverse", "magrittr", "haven", "data.table", "labelled", "here", "stringr", "rlang", "car",
         "caret", "DescTools", "stargazer", "kableExtra", "janitor")
have = want %in% rownames(installed.packages())
if ( any(!have) ) { install.packages( want[!have] ) }
junk <- lapply(want, library, character.only = TRUE)
options(scipen = 99)

rm(list = ls())

# Source the general workflow # ========================================================================

source(here('Scripts', 'synteval_scripts', 'Synteval_gen.R'))




```



\newpage
# Cyprus

```{r echo=FALSE, warning=FALSE, message=FALSE}

```

Synthetic variables have been estimated for the full set of Cypriot parties available in the original 
2019 EES Cypriot voter study (see Table \ref{table:tab_4_8}) <!-- table made with relprty_df-->. 


Full OLS models converge and coefficients do not show any particular issue. On the contrary, three out 
of six logit models do present inflated standard errors for some of the coefficients of interest, in 
particular: 


## Models fit 

In terms of model fit, OLS regression models vary in a range of the coefficient of determination ($R^2$)
values between `r ...` for party `r ...` (`r ...`) and `r ...` for party `r ...` (`r ...`). Contrasting 
Akaike information criterion (AIC) full model values with null model values it is possible to see how in 
3 cases out of 6 null models do show an equivalent or better fit than full models <!-- Re-check this line and insert proper R code -->

## Regression models results {-}

OLS full models estimating synthetic variables for 

## Anova tables {-}

```{r, results='asis', echo=F}

# options(xtable.comment = FALSE)
# xtable::xtable(anova_lst[[1]])
anova_df <- anova_lst %>% do.call('rbind',.) %>% .[c(1:4),]

kableExtra::kable(anova_df) %>% 
   kableExtra::kable_paper() %>% 
  kableExtra::pack_rows('G1',1,2) %>% 
  kableExtra::pack_rows('G1',3,4) 

```

# Regression tables {-}


```{r, results='asis', echo=F}

stargazer::stargazer(fullmod_lst$OLS, type = 'latex', 
                     column.labels = as.character(relprty_df$Q7),
                     dep.var.labels = 'PTV',
                     star.cutoffs = c(0.05, 0.01, 0.001),
                     omit.stat=c("f", "ser"),
                     header = F,
                     style = 'ajps')
```

```{r, results='asis', echo=F}

stargazer::stargazer(fullmod_lst$logit, type = 'latex', 
                     column.labels = as.character(relprty_df$Q7),
                     dep.var.labels = 'Vote choice',
                     star.cutoffs = c(0.05, 0.01, 0.001),
                     header = F,
                     style = 'ajps')
```