---
title: Summary of Synthetic Variables Estimation 
subtitle: EES 2019 Voter Study (Belgian sample)
author: Matthias Körnig
date: 18.04.2022 
toc: false
output: 
  bookdown::pdf_document2:
    includes:
      in_header: eval_header.tex
urlcolor: RedOrange
---

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

# Load 'here' for sourcing # - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - #
library('here')

# Source the general workflow # - - - - - - - - - - - - - - - - - - - - - - - - - - - - -#
source(here('Scripts', 'synteval', 'Synteval_gen.R'))

```

\newpage
# Belgium

```{r echo=FALSE, warning=FALSE, message=FALSE, , results='hide'}
# Source the Belgian synteval script # - - - - - - - - - - - - - - - - - - - - - - - - - #

source(here('Scripts', 'synteval', 'country_spec', 'EES2019_be_synteval.R'))

```

Synthetic variables have been estimated for the full set of Belgian parties available in the original 
2019 EES Belgian voter study selected according to the criteria stated in the EES 2019 SDM codebook (
for the criteria see Sect. XXX; for the relevant parties see Tables \ref{table:relprty_tab_be_du} and \ref{table:relprty_tab_be_fr}).
Note that the Belgian sample is splitted according to the two electoral colleges of Belgium, namely the 
Dutch and the French electoral college. 

```{r echo=FALSE, warning=FALSE, message=FALSE}
options(knitr.kable.NA = 'NA')
options(knitr.table.format = "latex")

#names(relprty_df) <- c('Dep. Var.', 'Party', 'Party name (eng)', 'El. Col.')

relprty_df %>% 
  filter(elcoll == 'DU-el') %>%
  select(depvar, partycode, partyname_eng, -elcoll) %>%
  rename('Dep. Var.' = depvar, 'Party' = partycode, 'Party name (eng)' = partyname_eng) %>%
  kable(caption = "Belgian relevant parties in Dutch electoral college \\label{table:relprty_tab_be_du}", booktabs = T, 
        align = c('l', 'c', 'l')) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

relprty_df %>% 
  filter(elcoll == 'FR-el') %>%
  select(depvar, partycode, partyname_eng, -elcoll) %>%
  rename('Dep. Var.' = depvar, 'Party' = partycode, 'Party name (eng)' = partyname_eng) %>%
  kable(caption = "Belgian relevant parties in French electoral college \\label{table:relprty_tab_be_fr}", booktabs = T, 
        align = c('l', 'c', 'l')) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

Full OLS models converge and coefficients do not show any particular issue (see Table 
\ref{table:full_ols_be_du} and Table \ref{table:full_ols_be_fr}). 

For the Dutch electoral college:
In terms of model fit, the adjusted coefficient of determination ($R^2$) values vary between 
a minimum value of `r ols_df[['DU-el']] %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['Adj_Rsq']]` 
for party `r ols_df[['DU-el']] %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partycode']]` 
(`r ols_df[['DU-el']] %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of `r ols_df[['DU-el']] %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['Adj_Rsq']]`
for party `r ols_df[['DU-el']] %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partycode']]`
(`r ols_df[['DU-el']] %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for full OLS models and null 
models shows that in all 7 cases out of 7 null models perform better than full ones (see Table 
\ref{table:ols_aic_be_du}).

For the French electoral college:
In terms of model fit, the adjusted coefficient of determination ($R^2$) values vary between 
a minimum value of `r ols_df[['FR-el']] %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['Adj_Rsq']]` 
for party `r ols_df[['FR-el']] %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partycode']]` 
(`r ols_df[['FR-el']] %>% filter(model=='full') %>% filter(Adj_Rsq==min(Adj_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of `r ols_df[['FR-el']] %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['Adj_Rsq']]`
for party `r ols_df[['FR-el']] %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partycode']]`
(`r ols_df[['FR-el']] %>% filter(model=='full') %>% filter(Adj_Rsq==max(Adj_Rsq)) %>% .[['partyname_eng']]`). 
Moreover, the difference between Akaike Information Criterion (AIC) values for full OLS models and null 
models shows that in all 7 cases out of 7 null models perform better than full ones (see Table 
\ref{table:ols_aic_be_fr}).

```{r echo=FALSE, warning=FALSE, message=FALSE}

colnames(ols_aic[['DU-el']]) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')
colnames(ols_aic[['FR-el']]) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')

ols_aic[['DU-el']] %>% 
  kable(caption = "Akaike Information Criterion values for OLS full and null models 
        \\label{table:ols_aic_be_du}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

ols_aic[['FR-el']] %>% 
  kable(caption = "Akaike Information Criterion values for OLS full and null models 
        \\label{table:ols_aic_be_fr}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))


```

Also all seven logistic regression models in the Dutch electoral college show no issue (see Table \ref{table:full_logit_be_du})
On the contrary, one out of seven logistic regression models in the French electoral college (see Table \ref{table:full_logit_be_fr}) show inflated standard errors for some of the coefficients of interest: 

* Model 26a: D8_rec, EDU_rec, D7_rec;

Model 26a of the French electoral college presents a more problematic profile, since it affects the models constant terms with its inflated standard errors.

Inflated standard errors are due to separation issues. In short:

* No respondents from rural areas voted for party 212 (Table \ref{table:crosstab_1_be});

* No low and high educated respondents voted for party 212 (Table \ref{table:crosstab_2_be})

* No upper class respondents voted for party 212 (Table \ref{table:crosstab_3_be}); 

As a consequence, a constrained version of model 26a without said variables was 
estimated and contrasted with the original, full model. Likelihood-ratio test results show 
that $H_0$ (namely, that the constrained model does not fit better than the full model) cannot be rejected at p<0.05
(see Table \ref{table:lrtest_1_be}). Consequently, synthetic variables for respondents' vote choice for 
party 212 have been predicted relying on the constrained model. 

```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = '')

anova_lst %>%
  kable(caption = "Likelihood-ratio Test between Model 26a (Unconstrained) and Model 26b (Constrained)
                  \\label{table:lrtest_1_be}", booktabs = F, ) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))

```

In the case of the Dutch electoral college:
In terms of model fit, adjusted McFadden's pseudo $R^2$ values for the logistic full models vary between 
a minimum value of 
`r logit_df[['DU-el']] %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)` 
for party `r logit_df[['DU-el']] %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partycode']]` 
(`r logit_df[['DU-el']] %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of 
`r logit_df[['DU-el']] %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)`
for party `r logit_df[['DU-el']] %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partycode']]`
(`r logit_df[['DU-el']] %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`). 

In the case of the Fench electoral college:
In terms of model fit, adjusted McFadden's pseudo $R^2$ values for the logistic full models vary between 
a minimum value of 
`r logit_df[['FR-el']] %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)` 
for party `r logit_df[['FR-el']] %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partycode']]` 
(`r logit_df[['FR-el']] %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==min(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`) 
and a maximum of 
`r logit_df[['FR-el']] %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['Adj_Ps_Rsq']] %>% round(.,3)`
for party `r logit_df[['FR-el']] %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partycode']]`
(`r logit_df[['FR-el']] %>% filter(model=='full') %>% filter(Adj_Ps_Rsq==max(Adj_Ps_Rsq)) %>% .[['partyname_eng']]`).


```{r echo=FALSE, warning=FALSE, message=FALSE}

colnames(logit_aic[['DU-el']]) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')
colnames(logit_aic[['FR-el']]) <- c('Dep. Var.', 'Party', 'Full Mod.', 'Null Mod.', 'Diff. (Full-Null)')


logit_aic[['DU-el']] %>% 
  kable(caption = "Akaike Information Criterion values for logistic full and null models 
        \\label{table:logit_aic_be_du}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position'))
           

logit_aic[['FR-el']] %>% 
  kable(caption = "Akaike Information Criterion values for logistic full and null models 
        \\label{table:logit_aic_be_fr}", booktabs = T, 
        align = c('l', 'c', rep('r',3))) %>% 
  kable_styling(latex_options = c('striped', 'hold_position')) %>% 
  footnote(symbol = 'AIC value of 212 refers to Model 26b (constrained).',
           threeparttable = T,
           footnote_as_chunk = T)
```


```{r echo=FALSE, warning=FALSE, message=FALSE}

options(knitr.kable.NA = 'NA')

tabs[[1]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 212 and respondents' area of residency 
                   \\label{table:crosstab_1_be}", booktabs = F) %>%  #  align = c('l', 'c', rep('r',3))
  kable_styling(latex_options = c('striped'))

tabs[[2]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 212 and respondents' education
                   \\label{table:crosstab_2_be}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))

tabs[[3]] %>% 
  kable(caption = "Cross tabulation between vote choice for party 212 and respondents' subjective social class
                   \\label{table:crosstab_3_be}", booktabs = F) %>% 
  kable_styling(latex_options = c('striped'))


```


```{r, results='asis', echo=F}

stargazer::stargazer(finalmod_lst[['DU-el']]$OLS,
                     title = 'Vote choice for a relevant party according to respondents 
                       socio-demographic characteristics at Dutch Electoral College (Ordinary square models)',
                     label = 'table:full_ols_be_du',
                     type = 'latex',
                     column.labels = c('207', '201', '204', '206', '203', '202', '205'),
                     dep.var.labels.include = F,
                     star.cutoffs = c(0.05, 0.01, 0.001),
                     omit.stat=c("f", "ser"),
                     header = F,
                     style = 'ajps')

logit_regtab <-
  stargazer::stargazer(finalmod_lst[['DU-el']]$logit,
                     title = 'Vote choice for a relevant party according to respondents 
                       socio-demographic characteristics at Dutch Electoral College (Logistic regression models)',
                     label = 'table:full_logit_be_du',
                     type = 'latex',
                     column.labels = c('207', '201', '204', '206', '203', '202', '205'),
                     dep.var.labels.include = F,
                     star.cutoffs = c(0.05, 0.01, 0.001),
                     omit.stat=c("f", "ser"),
                     header = F,
                     style = 'ajps') %>%
capture.output() 


logit_regtab[9] %<>%
  gsub('Model 1', 'Model 8',.) %>%
  gsub('Model 7', 'Model 14',.) %>%
  gsub('Model 6', 'Model 13',.) %>% 
  gsub('Model 5', 'Model 12',.) %>% 
  gsub('Model 4', 'Model 11',.) %>% 
  gsub('Model 3', 'Model 10',.) %>% 
  gsub('Model 2', 'Model 9',.) 

cat(logit_regtab, sep = "\n")


ols_regtab <-
  stargazer::stargazer(finalmod_lst[['FR-el']]$OLS,
                       title = 'Vote choice for a relevant party according to respondents
                         socio-demographic characteristics at French Electoral College (OLS regression models)',
                       label = 'table:full_ols_be_fr',
                       type = 'latex',
                       no.space = T, # to remove the spaces after each line of coefficients
                       column.sep.width = '0.5pt', # to reduce column width
                       column.labels = c('208', '209', '210', '211', '212', '213', '214'),
                       dep.var.labels.include = F,
                       star.cutoffs = c(0.05, 0.01, 0.001),
                       omit.stat=c("f", "ser"),
                       header = F,
                       style = 'ajps') %>%
capture.output()

ols_regtab[9] %<>%
  gsub('Model 1', 'Model 15',.) %>%
  gsub('Model 2', 'Model 16',.) %>%
  gsub('Model 7', 'Model 21',.) %>%
  gsub('Model 6', 'Model 20',.) %>%
  gsub('Model 5', 'Model 19',.) %>%
  gsub('Model 4', 'Model 18',.) %>%
  gsub('Model 3', 'Model 17',.)

cat(ols_regtab, sep = "\n")

logit_regtab2 <-
  stargazer::stargazer(finalmod_lst[['FR-el']]$logit,
                     title = 'Vote choice for a relevant party according to respondents 
                       socio-demographic characteristics at French Electoral College (Logistic regression models)',
                     label = 'table:full_logit_be_fr',
                     type = 'latex',
                     no.space = T, # to remove the spaces after each line of coefficients
                     column.sep.width = '0.5pt', # to reduce column width
                     font.size = 'footnotesize', # to make font size smaller
                     column.labels = c('208', '209', '210', '211', '212', '212', '213', '214'),
                     dep.var.labels.include = F,
                     star.cutoffs = c(0.05, 0.01, 0.001),
                     omit.stat=c("f", "ser"),
                     header = F,
                     style = 'ajps') %>%
capture.output() 

logit_regtab2[10] %<>%
  gsub('Model 2', 'Model 23',.) %>%
  gsub('Model 8', 'Model 28',.) %>%
  gsub('Model 7', 'Model 27',.) %>%
  gsub('Model 6', 'Model 26b',.) %>%
  gsub('Model 5', 'Model 26a',.) %>%
  gsub('Model 4', 'Model 25',.) %>%
  gsub('Model 3', 'Model 24',.) %>%
  gsub('Model 1', 'Model 22',.)

cat(logit_regtab2, sep = "\n")
  

```
